### 2019-03-21 Sections/economics_of_the_quantum_internet.tex
minor
Dad's quotes

The key observation is that a unit of computation (FLOP) does not carry over time. It must be utilised immediately and cannot be stored for future use. This simplifies the forward price of a unit of computation to simply be the future spot price, discounted by the risk-free RoR, yielding the forward contract pricing model for quantum computing time-shares,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in a unit of network runtime at future time $T$ is,
\begin{align}
F(T) &= e^{-r_\mathrm{rf}T} L(T)\nonumber\\
&=\frac{e^{\gamma_\mathrm{ror}-r_\mathrm{rf}T} C_0{\gamma_C}^{-T}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^T)}.
\end{align}
\end{definition}

@@

When implementing quantum computations characterised by completely general computational scaling functions\index{Computational scaling functions}, $f^{(X,Y)}_\mathrm{sc}$ (which in general can be distinct for the two players, $X$ and $Y$), when using an \textsc{Isolation} strategy, the respective payoff matrix elements are simply given by,
\begin{align}\label{eq:util_payoff_iso}
\textsc{Payoff} = (f^{(X)}_\mathrm{sc}(n_X),f^{(Y)}_\mathrm{sc}(n_Y)),
\end{align}
where payoff matrix elements are assumed to be in units of classical-equivalent processing time\footnote{There's nothing unique or special about using classical-equivalent computational power as our utility measure. Any other measure of `payoff' could be equally well justified, depending on circumstance. For example, one could instead represent utility in terms of the monetary value of computational power. In that case, we simply need to transform the payoff matrix elements using the cost of computation\index{Cost of computation} identity presented in Post.~\ref{post:cost_comp}.} (i.e FLOPs), and resource-sharing is based on the methodology for arbitrage-free time-share allocation presented in Sec.~\ref{sec:arb_free_time_share}.

@@

This is easily logically generalised to an arbitrary multi-player setting, in which case the transformation becomes,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{License}}{\longrightarrow} \sum_{j=1}^N r_{j\to i} f_\mathrm{sc}^{(i)}(n_j),
\end{align}
where there are $N$ players, all engaging with one another using licensing only. Here, $r_{i\to j}$ denotes the proportion of $i$'s compute-time licensed to $j$, which are normalised for all users such that,
\begin{align}
\sum_{j=1}^N r_{i\to j} \leq 1\,\,\forall\,i.	\
\end{align}

@@

>>>>

The key observation is that a unit of computation (FLOP) does not carry over time. It must be utilised immediately and cannot be stored for future use. This simplifies the forward price of a unit of computation to simply be the future spot price, discounted by the risk-free RoR, yielding the forward contract pricing model for quantum computing time-shares,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in a unit of network runtime at future time $T$ is,
\begin{align}
F(T) &= e^{-r_\mathrm{rf}T} L(T)\nonumber\\
&=\frac{e^{(\gamma_\mathrm{ror}-r_\mathrm{rf})T} C_0{\gamma_C}^{-T}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^T)}.
\end{align}
\end{definition}

@@

When implementing quantum computations characterised by completely general computational scaling functions\index{Computational scaling functions}, $f^{(X,Y)}_\mathrm{sc}$ (which in general can be distinct for the two players, $X$ and $Y$), when using an \textsc{Isolation} strategy, the respective payoff matrix elements are simply given by,
\begin{align}\label{eq:util_payoff_iso}
\textsc{Isolation} = \begin{pmatrix}
 	f^{(X)}_\mathrm{sc}(n_X)\\
 	f^{(Y)}_\mathrm{sc}(n_Y)
 \end{pmatrix},
\end{align}
where payoff matrix elements are assumed to be in units of classical-equivalent processing time\footnote{There's nothing unique or special about using classical-equivalent computational power as our utility measure. Any other measure of `payoff' could be equally well justified, depending on circumstance. For example, one could instead represent utility in terms of the monetary value of computational power. In that case, we simply need to transform the payoff matrix elements using the cost of computation\index{Cost of computation} identity presented in Post.~\ref{post:cost_comp}.} (i.e FLOPs), and resource-sharing is based on the methodology for arbitrage-free time-share allocation presented in Sec.~\ref{sec:arb_free_time_share}.

@@

This is easily logically generalised to an arbitrary multi-player setting, in which case the transformation becomes,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{License}}{\longrightarrow} \sum_{j=1}^N r_{j\to i} f_\mathrm{sc}^{(i)}(n_j),
\end{align}
where there are $N$ players, all engaging with one another using licensing only. The $r_{i\to j}$ parameters are normalised for all users such that,
\begin{align}
\sum_{j=1}^N r_{i\to j} \leq 1\,\,\forall\,i.
\end{align}

@@

\subsubsection{Adversarial enhancement}\index{Adversarial enhancement}

\famousquote{In savage countries they eat one another, in civilised ones they deceive one another; and that is what people call the way of the world!}{Arthur Schopenhauer}

\comment{To do}

\begin{itemize}
\item ...	
\end{itemize}

### 2019-03-21 Sections/essay_geostrategic_quantum_politics.tex
+quotes, formatting
Dad's quotes

\dropcap{C}{omputation} is a commodity -- likely to be one of the most valuable of the 21st century economy -- and with any valuable, sought after commodity comes geostrategic politics. World powers fight wars, apply sanctions and use political leverage against one another to secure access to traditional commodities essential to economic progress and competitive advantage. It is to be expected that computation will be no different.

@@

The central point to note is the computational leverage phenomena associated with the quantum internet -- unification of resources is better for all. However, it is important to be cognisant that the leverage gained by parties unifying their resources with the cloud is asymmetric, biased in favour of the weaker parties. That is, despite the fact that all players benefit from unification, smaller players relatively have more to gain. While this asymmetric computational leverage may seem favourable for the weaker parties, it also places them in a compromised situation whereby the threat of a major player expelling the smaller one from the network\footnote{Quantum internexit.} creates asymmetric political leverage in the opposite direction. A major player will have relatively little to lose under the expulsion of a smaller player. But the smaller player could suffer immensely in the relative power of their computational assets.

>>>>

\famousquote{What the United States fears the most is taking casualties. The loss of one super carrier would cost the US the lives of 5000 service men and women. Sinking two would double that toll. We'll see how frightened America is.}{Admiral Lou Yuan}
\newline

\dropcap{C}{omputation} is a commodity -- perhaps the most valuable of all in the 21st century economy -- and with any valuable, sought after commodity comes geostrategic powerplay. World powers fight wars, apply sanctions and use political leverage against one another to secure access to traditional commodities essential to economic progress and competitive advantage. It is to be expected that computation will be no different.

@@

The central point to note is the computational leverage phenomena associated with the quantum internet -- unification of resources is better for all. However, it is important to be cognisant that the leverage gained by parties unifying their resources with the cloud is asymmetric, biased in favour of (or against in an adversarial context) the weaker parties. That is, despite the fact that all players benefit from unification, smaller players relatively have more to gain. While this asymmetric computational leverage may seem favourable for the weaker parties, it also places them in a compromised situation whereby the threat of a major player expelling the smaller one from the network\footnote{Quantum internexit.} creates asymmetric political leverage in the opposite direction. A major player will have relatively little to lose under the expulsion of a smaller player. But the smaller player could suffer immensely in the relative power of their computational assets.
